Context-dependent consequences of including lagged effects in demographic models

### 2022-03-07 docs/paper.Rmd
rough out some text

2.  It has long been recognized that there is the potential for lagged effects.
    Now there's evidence for that [@scottInteractiveEffectsDrought2019].

@@

Methods text.

@@

@@

We thank **,** \_, \_\_\_ and \_\_\_ anonymous reviewers for helpful discussions and comments on the manuscript.
Financial support was provided by the U.S.
National Science Foundation (awards \_\_\_\_, and \_\_\_\_).
The authors delcare no conflicts of interest.

>>>>

2.  It has long been recognized that there is the potential for lagged effects.
    Now there's evidence for that [@eversLaggedDormantSeason2021; @scottDelayedEffectsClimate2022].

@@

## Modeling vital rates

Used 10 yr demographic dataset for modeling post-seedling survival, growth, and flowering; seedling survival and growth.
For post-seedlings, all vital rates were modeled as a smooth function of log(size_t) using a penalized spline in generalized additive models (GAMs) using the `mgcv` package [@mgcv].

-   Where the rest of the fecundity data comes from

For stochastic IPMs, we took two approaches.
In the first approach, we added a random intercept for year to all post-seedling vital rates GAMs, when supported by the data (i.e. p-value for random effect \< 0.05) <!--# something about how you can actually use p-values for random effects fit with mgcv -->.
Then, we used kernel-resampled ipms to generate kernels for each year of data and iterate the IPM by drawing from these randomly.
Equivalent to "matrix shuffling" approach in matrix population models (CITATION).
In the second approach, we modeled the impacts of the environment on vital rates explicitly.
We calculated the standardized precipitation evapotranspiraion index (SPEI).
We modeled effects of SPEI on post-seedling survival, growth, and flowering probability using distributed lag non-linear models fit as two dimensional tensor product splines [@scottDelayedEffectsClimate2022].
Then these models were incorporated into a parameter-resampled IPM.
To iterate such an IPM, a random sequence of SPEI values is created by re-sampling the observed monthly SPEI data.
Then, 36 month lags are calculated for each year starting in February (the month of the demographic census).
These values are then used to iterate the IPM.

IPMs built and iterated with the @ipmr package.

Use fitted_samples() for bootsrapping CIs around lambda?

@@

-   table of vital rate models.
    Which vital rate, which IPM, ∆AIC, model edf.

-   table of lambdas.
    2 habitats x 3 (4?) IPMs

-   figure of PVA??
    Conceptual diagram instead?

@@

We thank **,** \_, \_\_\_ and \_\_\_ anonymous reviewers for helpful discussions and comments on the manuscript.
We thank Sam Levin for his help with the `ipmr` package.
Financial support was provided by the U.S.
National Science Foundation (awards \_\_\_\_, and \_\_\_\_).
The authors declare no conflicts of interest.
